### 2016-03-15 paper/result_optical_flow.tex
figure change

\begin{figure}[!ht]
  \centering
  \includegraphics[width=0.8\columnwidth]{figure/optical_flow_convergence.png}
  \caption{Energy plots for optical flow estimation. SF-MF has the best
 performance due to its solution sharing strategy.}\label{fig:optical_flow_convergence}
\end{figure}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_PFM_threads.png}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_SF_MF_threads.png}
  \end{subfigure}
  \caption{Energy plots per thread. Left: Parallel Fusion  
    Move (PFM). Right: SF-MF(ours).}
  \label{fig:optical_flow_by_threads}  
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.49\columnwidth}
\includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
\end{subfigure}
\begin{subfigure}[b]{0.49\columnwidth}
\includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
\end{subfigure}
\caption{Energy
  plots for optical flow under difference configurations. Left:
  varying $\beta$; right: varying solution sharing
  frequencies. Solution sharing achieves better convergence, but
  sharing too many solutions (larger $\beta$) or sharing solutions too
  frequently (less $k$) slows down the convergence, as it reduces the
  time for exploration.} \label{fig:opticalflow_configuration}
\end{figure}

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[width=0.8\columnwidth]{figure/optical_flow_convergence.png}
  \caption{Energy plots for the optical flow problem. SF-MF has the best
    performance due to its solution sharing strategy.}\label{fig:optical_flow_convergence}
\end{figure}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_PFM_threads.png}
  \end{subfigure}  
  \begin{subfigure}[b]{0.49\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure/optical_flow_SF_MF_threads.png}
  \end{subfigure}
  \caption{Energy plots per thread for the optical flow problem. Left: Parallel Fusion  
    Move (PFM). Right: SF-MF(ours).}
  \label{fig:optical_flow_by_threads}  
\end{figure}

@@

\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.49\columnwidth}
\includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
\end{subfigure}
\begin{subfigure}[b]{0.49\columnwidth}
\includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
\end{subfigure}
\caption{Energy
  plots for optical flow under different configurations. Left:
  varying $\beta$; Right: varying solution sharing
  frequencies. Solution sharing achieves better convergence, but
  sharing too many solutions (larger $\beta$) or sharing solutions too
  frequently (less $k$) slows down the convergence, as it reduces the
  time for exploration.} \label{fig:opticalflow_configuration}
\end{figure}
